### 2024-11-06 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

To build the community trait space, we undertook a PCA including all $118$ species, which we then subset to calculate the trait space for the historic and extant datasets.
We selected the first $5$ axes to represent the trait spaces that explained at least 97.5\% of the variance in each specific group (all, historic and extant species)
We applied the same procedure as for the simulated data by simulating a null mechanism to compare to the observed ones by randomly removing $55$ and $81$ species for each stressor and scaling the results proportionally to this null mechanism (as described above).

>>>>

To build the community trait space, we undertook a PCA including all $118$ species, which we then subset to calculate the trait space for the historic and extant datasets.
We selected the first $5$ axes to represent the trait spaces that explained at least 95\% of the variance in each specific group (historic and extant species - see supplementary figure 7; following recommendations of \citealt{pigot2020macroevolutionary} and dimensionality selection method from \citealt{guillerme2023innovation}).
We applied the same procedure as for the simulated data by simulating a null mechanism to compare to the observed ones by randomly removing $55$ and $81$ species for each stressor and scaling the results proportionally to this null mechanism (as described above).
